Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-24 prop_iop.tex
prop_iop.tex Updating here and there...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantum Interval-valued Probability Measures}

@@

\noindent It is easy to establish that quantum interval-valued probability
measures generalize conventional quantum probability measures. In
particular, any quantum probability measure can be recast as an interval-valued
measure using arbitrary small intervals as discussed in \ref{sec:Real-and-Interval}.
However, to simplify our discussion, we will focus on only three intervals
$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\begin{equation} 
\iota(x)=\cases{ 
\necess & if $x=1$ ;\\ 
\imposs & if $x=0$ ;\\ 
\unknown & otherwise. 
}\label{eq:homomorphism} \end{equation}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figure1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$. $\ket{0}$
is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$
for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
\end{figure}
For example, figure~\ref{fig:three-dimensional-3-value} plots the
1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$.
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question.\footnote{\yutsung{Actually, $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$ is quite
informative. Since $\iota\left(\mu_{\ket{0}}^{B}(P)\right)=\necess$
if and only if $P=\proj{0}$, we know the core of $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
is exactly $\left\{ \mu_{\ket{0}}^{B}\right\} $. The quantum interval-valued
probability measure for an experimenter with no prior knowledge should
be $\bar{\mu}(P)=\unknown$ for every projection~$P$.}} Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum interval-valued probability measure, i.e.,
given observations done with finite resources. In the case that the
intervals are infinitely precise, the question reduces to Gleason's
theorem which states that the state of the quantum system is uniquely
determined by the probability measure. But surely the less resources
are available, the less precise the intervals, and the less we expect
to know about the state of the system. To formally state and answer
this question we begin with defining the \emph{core} and \emph{convexity}
of a probability measure as follows.

>>>>

\section{Cryptodeterminism}

Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

\begin{definition}[Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
the set of events~$\events$, a \emph{cryptodeterministic measure}
is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $ such
that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$, 
\item $\pmeas(\Omega)=1$, 
\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
where $\Omega\backslash E$ is the complement event of $E$, and 
\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
\end{itemize}
\end{definition}

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
of the prefect prediction, a cryptodeterministic measure can model
the belief of an event which has already happened. For example, if
we toss the coin in example~\ref{ex1}, and see $HH$, our belief
of which event has happened can be model by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & 0\\
\bar{\mu}(\{HH\}) & = & 1\\
\bar{\mu}(\{HT\}) & = & 0\\
\bar{\mu}(\{TH\}) & = & 0\\
\bar{\mu}(\{TT\}) & = & 0\\
\bar{\mu}(\{HH,HT\}) & = & 1\\
\bar{\mu}(\{HH,TH\}) & = & 1\\
\bar{\mu}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & 0\\
\bar{\mu}(\{HT,TT\}) & = & 0\\
\bar{\mu}(\{TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

Raised by Einstein, Podolsky, and Rosen~\cite{EPR1935,peres1995quantum},
it was a famous question whether quantum mechanics have any change
to be improved and predict perfectly. One of the ``no'' answer was
due to the Kochen-Specker theorem.

\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}Given
a Hilbert space of dimension~$d\ge3$, there is no cryptodeterministic
measure~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $.\end{thm}

Although sharing a lot of similarity, the Kochen-Specker theorem highlight
the difference between quantum and classical measures. When we think
a cryptodeterministic measure as a model of pasted events, the Kochen-Specker
theorem also consistent with the usual interpretation of the quantum
theory: we should not ask whether an event happened or not if an event
is incompatible with the event really happened; events compatible
with the event really happened are the only events which are askable.

\section{Quantum Interval-valued Probability}

%%%%%

\subsection{Quantum Interval-valued Probability Measures}

@@

\noindent It is easy to establish that quantum interval-valued probability
measures generalize conventional quantum probability measures. In
particular, any quantum probability measure can be recast as an interval-valued
measure using arbitrary small intervals as discussed in \ref{sec:Real-and-Interval}.
However, to simplify our discussion, we will focus on only three intervals
$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\begin{equation} 
\iota(x)=\cases{ 
\necess & if $x=1$ ;\\ 
\imposs & if $x=0$ ;\\ 
\unknown & otherwise. 
}\label{eq:homomorphism} \end{equation}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figure1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$. $\ket{0}$
is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$
for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
\end{figure}
For example, figure~\ref{fig:three-dimensional-3-value} plots the
1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$.
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question.\footnote{\yutsung{Actually, $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$ is quite
informative. Since $\iota\left(\mu_{\ket{0}}^{B}(P)\right)=\necess$
if and only if $P=\proj{0}$, we know the core of $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
is exactly $\left\{ \mu_{\ket{0}}^{B}\right\} $. The quantum interval-valued
probability measure for an experimenter with no prior knowledge should
be $\bar{\mu}(P)=\unknown$ for every projection~$P$.}}

Similarly, we can recast the result of cryptodeterminism to quantum
interval-valued probability measures as well. In another word, for
any classically event space~$\events$,there is always a classical
interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
However, given a Hilbert space of dimension~$d\ge3$, there is no
quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
by the Kochen-Specker theorem. The Kochen-Specker theorem provides
an example that quantum interval-valued probability measures behave
differently from the classical one, and the convexity and core in
the next section provides another example that quantum interval-valued
probability measures behave unexpectedly.

%%%%%

\subsection{Convexity and Core}

\noindent Formally, we can ask: what can we deduce about the state
of a quantum system given a quantum interval-valued probability measure,
i.e., given observations done with finite resources. In the case that
the intervals are infinitely precise, the question reduces to Gleason's
theorem which states that the state of the quantum system is uniquely
determined by the probability measure. But surely the less resources
are available, the less precise the intervals, and the less we expect
to know about the state of the system. To formally state and answer
this question we begin with defining the \emph{core} and \emph{convexity}
of a probability measure as follows.
